J-Study manuscript

### 2023-03-05 writing/ms.Rmd
start to add extra stat reports, bayes fact alone

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
require(tidyverse)
require(magrittr)
load(here::here("ignore", "data", "plots_ms.rda"))
```

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
require(tidyverse)
require(magrittr)
require(rlang)
load(here::here("ignore", "data", "preplots.rda")) # For the model params
load(here::here("ignore", "data", "plots_ms.rda"))

signif_digits <- 3L
```

```{r setup-extra-stat-reports}
summarize_report <- function (data, col, ..., stat_name = "", unit_name = "", digs = signif_digits) {
  if (unit_name != "") unit_name %<>% paste0(" ", .)
  glue_in = if_else(stat_name != "",
                    "{stat_name} = {a}{unit_name}, 95% CI [{b}, {c}]",
                    "{a}{unit_name}, 95% CI [{b}, {c}]")

  col_chr = as_name(enexpr(col))
  group_cols = enexprs(...)

  data %<>%
    select(iteration, !!!group_cols, starts_with(col_chr)) %>%
    pivot_longer(cols = starts_with(col_chr),
                 names_to = "metric_type",
                 values_to = "value",
                 names_prefix = glue::glue("{col_chr}_"))

  if (!is.null(group_cols)) {
    data %<>% group_by(!!!group_cols, metric_type)
  } else {
    data %<>% group_by(metric_type)
  }
  data %<>%
    summarize(avg = mean(value, na.rm = T),
              q025 = quantile(value, .025, na.rm = T),
              q975 = quantile(value, .975, na.rm = T)) %>% 
    mutate(across(c("avg", "q025", "q975"),
                  \(x) formatC(signif(x, digits = digs), digits = digs, format = "fg", flag = "#", mode = "double")),
           txt_apa = pmap_chr(list(avg, q025, q975),
                              \(a, b, c) {glue::glue(glue_in)}
           ),
           across(c("avg", "q025", "q975"), as.numeric))

  return (data)
}

coefs_fact_by_pic <- preplot_params_fact_by_pic %>%
  summarize_report(col = estimate, term, stat_name = "beta")

coefs_fact_by_source <- preplot_params_fact_by_source %>%
  summarize_report(col = estimate, term, stat_name = "beta")
```

@@

Interaction coefficient: `r coefs_fact_by_pic %>% filter(term == "resp_pic:j_score") %>% pull(txt_apa)`

@@

Interaction coefficient: `r coefs_fact_by_source %>% filter(term == "resp_source:j_score") %>% pull(txt_apa)`
